Inferring the effective start dates of non-pharmaceutical interventions during COVID-19 outbreaks

### 2020-05-19 ms/ms.tex
better captions for ppc fig

%%% Fig PPC %%%
\begin{figure}[h]
    \centering
	\subcaption{Austria}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Austria_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Austria_ppc.pdf}
    \end{subfigure}
    %%%
	\subcaption{Belgium}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Belgium_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Belgium_ppc.pdf}
    \end{subfigure}
    %%%
	\subcaption{Denmark}    
     \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Denmark_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Denmark_ppc.pdf}
    \end{subfigure}
\end{figure}
    %%%
\begin{figure}
    \ContinuedFloat 
	\subcaption{France}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/France_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/France_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Germany}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Germany_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Germany_ppc.pdf}
    \end{subfigure}
    %%% 
	\subcaption{Italy}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Italy_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Italy_ppc.pdf}
    \end{subfigure}
    %%% 
	\subcaption{Norway}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Norway_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Norway_ppc.pdf}
    \end{subfigure}
\end{figure}
    %%%
\begin{figure}
    \ContinuedFloat   
	\subcaption{Spain}     
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Spain_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Spain_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Sweden}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Sweden_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Sweden_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Switzerland}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Switzerland_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Switzerland_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{United Kingdom}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/United_Kingdom_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/United_Kingdom_ppc.pdf}
    \end{subfigure}
    %%%
    \caption{
     \textbf{Figure S1. Posterior predictive plots.}
	}
	\label{fig:ppc}
\end{figure}

>>>>

%%% Fig PPC %%%
\begin{figure}[h]
    \centering
	\subcaption{Austria}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Austria_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Austria_ppc.pdf}
    \end{subfigure}
    %%%
	\subcaption{Belgium}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Belgium_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Belgium_ppc.pdf}
    \end{subfigure}
    %%%
	\subcaption{Denmark}    
     \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Denmark_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Denmark_ppc.pdf}
    \end{subfigure}
\end{figure}
    %%%
\begin{figure}
    \ContinuedFloat 
	\subcaption{France}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/France_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/France_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Germany}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Germany_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Germany_ppc.pdf}
    \end{subfigure}
    %%% 
	\subcaption{Italy}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Italy_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Italy_ppc.pdf}
    \end{subfigure}
    %%% 
	\subcaption{Norway}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Norway_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Norway_ppc.pdf}
    \end{subfigure}
\end{figure}
    %%%
\begin{figure}
    \ContinuedFloat   
	\subcaption{Spain}     
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Spain_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Spain_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Sweden}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Sweden_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Sweden_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Switzerland}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Switzerland_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Switzerland_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{United Kingdom}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/United_Kingdom_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/United_Kingdom_ppc.pdf}
    \end{subfigure}
    %%%
    \caption{
     \textbf{Figure S1. Posterior prediction check plots}
     Markers represent data ($\vec{X}$). Black line represent a smoothing of the data points using a Savitzky-Golay filter. Color lines represent posterior predictions from a model with fixed $\tau$, in red, and free $\tau$, in blue. These predictions are made by drawing 1,000 samples from the parameter posterior distribution and then generating a daily case count using the SEIR model in \autoref{eq:model}. Note the differences in the y-axis scale.}
	\label{fig:ppc}
\end{figure}
